---
title: "CV_example"
author: "Matthew Carroll"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(agricolae)
```
Set up fake data examples
```{r}
n_reps = 3
n_geno = 20
n_col = 10
n_row = 6

plot_num = n_reps*n_geno
plot_num1 = n_col * n_row 

#checking to make sure field design is correct
plot_num == plot_num1

```
```{r}
genotypes = c(1:n_geno)
reps = c(1:n_reps)
columns = c(1:n_col)
rows = c(1:n_row)

row_col = expand.grid(Columns = columns, Rows = rows)

replications = rep(reps,each = n_geno)

field_book = 
row_col%>%
  arrange(Rows,Columns)%>%
  mutate(Reps = replications)

#check to make sure the field desing is what you are expecting
field_book%>%
  ggplot(aes(x = Columns, y = Rows, fill = Reps))+
  geom_tile()+
  scale_fill_viridis_c()
```

Generate Random, within replication gentoype --> plot location
```{r}
count = 1
for (i in reps) {
  geno = sample(genotypes, size = n_geno)
  df = expand.grid(Reps = i, Genotype = geno)
  if(count == 1){
    Rep_geno = df
  }else{
    Rep_geno = rbind(Rep_geno, df)
  }
  count = count +1
}


Rep_geno
field_book
field_book$Genotype = Rep_geno$Genotype

#check that layout still looks correct
field_book%>%
  ggplot(aes(x = Columns, y = Rows, fill = Genotype))+
  geom_tile()

field_book%>%
  group_by(Genotype)%>%
  count()

field_book%>%
  group_by(Genotype,Reps)%>%
  count()
```
Simulating Genotypic effects
Rep Effects
Random effects

```{r}
population_mean = 60
SD = 10
genotype_effect = rnorm(n = n_geno, mean = population_mean, sd = SD)

rep_effect = c(-2,0,2)

Geno_df = as.data.frame(cbind(Genotype = genotypes, genotype_effect))
Rep_df = as.data.frame(cbind(Reps = reps, rep_effect))

#merging genotype and rep effects to field book
field_book = 
field_book%>%
  left_join(Geno_df)%>%
  left_join(Rep_df)

field_book

```
Random effects for each plot

```{r}
rand_mean = 0 
rand_sd = 5
rand_effects = rnorm(n = n_col*n_row, mean = rand_mean, sd = rand_sd)
rand_effects
field_book$rand_effect = rand_effects
field_book = 
field_book%>%
  mutate(Yield =genotype_effect + rep_effect +rand_effect  )

field_book
```

SD and CV calcs
https://en.wikipedia.org/wiki/Coefficient_of_variation
CV = sd/mean
when using a linear model SD should be based on the anova output, not on the entire SD but the unexplained error. 


```{r}
sd_phenotypic = sd(field_book$Yield)
mean_photypic = mean(field_book$Yield)
sd_phenotypic
mean_photypic

CV = sd_phenotypic/mean_photypic*100
CV
```

```{r}
field_book
```

Factor around genotype and reps becasue it is an integer and the linear model will try to run this as a slope and not an intercept

```{r}
lm_yield = lm(Yield ~ factor(Genotype) + factor(Reps), data = field_book)

lm_yield
summary(lm_yield)
anova(lm_yield)


CV_lm = sqrt(25.52)/mean_photypic*100
CV_lm
```
Check wiht Agricolae package
Soybean we use 15% as a threshold to keep or discard a trial 
This is the difference in keep or removing a location worth of data
```{r}

LSD.test(lm_yield,console = TRUE, trt = "factor(Genotype)")$statistics

cv.model(lm_yield)
```
LSD formula and explanation when their are different levels of replication
Gomes and Gomez page 201
```{r}
anova(lm_yield)


t_value = qt( p = .975, df = 38)
s2 = 25.51556
reps_1 = 3
reps_2 = 3
reps_add = (1/reps_1)+(1/reps_2)

t_value*sqrt(s2*(reps_add))

```
```{r}
new_field_book = field_book[-1,]
new_field_book  

lm_yield = lm(Yield ~ factor(Genotype) + factor(Reps),
              data = new_field_book )

anova(lm_yield)

LSD.test(lm_yield,console = TRUE, trt = "factor(Genotype)")$statistics
```


```{r}
t_value = qt( p = .975, df = 37)
s2 = 26.08329
reps_1 = 3
reps_2 = 3
reps_add = (1/reps_1)+(1/reps_2)

t_value*sqrt(s2*(reps_add))

```


How to make an RCBD desing in agrcolae

```{r}
design.rcbd(trt = genotypes, r = n_reps)
```


